---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sciencedb

<!-- badges: start -->

<!-- badges: end -->

The goal of **sciencedb** is to provide a user-friendly, programmatic R
interface to [ScienceDB](https://www.scidb.cn/) (Science Data Bank), a
global generalist data repository managed by the Computer Network
Information Center (CNIC) of the Chinese Academy of Sciences (CAS). As a
core platform for publishing, sharing, and accessing scientific data
from China and around the world, ScienceDB holds vast, high-value
datasets spanning multidisciplinary research domains.

`sciencedb` bridges this ecosystem with R workflow by allowing users to
search across up to 10,000 datasets by keywords, inspect dataset
metadata, and batch-downloads files directly into their local
environment with smart file management.

## Installation

You can install the development version of sciencedb from
[GitHub](https://github.com/) with:

``` r
# Recommended (fast installer)
# install.packages("pak")
pak::pak("jennyyzxu/sciencedb")

# Alternative
# install.packages("devtools")
devtools::install_github("jennyyzxu/sciencedb")
```

## Example

Below is a basic example demonstrating how an R user can aery multi-word
topics, evaluate dataset structure, and download data files locally:

```{r setup}
library(sciencedb)
```

1.  **Search for Datasets**

    Use `sdb_search()` to discover datasets using keywords. Because
    queries return deep multi-column metadata, fetching queries across
    thousands of records can take 15 to 30 seconds depending on network
    latency. The function returns a cleaned data frame where each row
    represents a dataset and includes 12 metadata attributes:

    | **Column** | **Description** |
    |----|----|
    | `Title` | Primary English dataset title (falls back to Chinese title if English is absent) |
    | `Author` | Semicolon-separated list of author names |
    | `Keyword` | Semicolon-separated domain keywords |
    | `Publish` | Official dataset release date |
    | `Doi` | Digital Object Identifier associated with the dataset |
    | `Taxonomy` | Scientific classification and subject taxonomy |
    | `Language` | Primary dataset language code (`en`, `zh`, etc.) |
    | `Introduction` | Full dataset abstract and methodological description |
    | `Access` | Rights/conditions (`PUBLIC`, `RESTRICTED`, or `EMBARGO`) |
    | `Views` | Historical platform page view counts |
    | `Downloads` | Total file download metric |
    | `Cstr` | China Science and Technology Resource identifier |

```{r}
# Search for datasets related to attachment
results <- sdb_search(keyword = "attachment")

# Preview core metadata columns for the top 3 results
head(results)
```

2.  **Inspect Dataset Details**

    Once a dataset or DOI of inerest is identified from the search
    results, use `sdb_dive()` to pull full file lists, directory
    hierarchies, and version details:

```{r}
# Retreive full metadata and file information for a specific dataset
info <- sdb_dive(doi = "10.57760/sciencedb.o00115.00098")

# Preview taxonomy
info[[1]]$taxonomy
```

3.  **Download Files**

    Use `sdb_download()` to download dataset files to your local
    directory. The function automatically rename files (e.g.,
    data(1).csv) if duplicates exist:

```{r}
# Download all files into a local folder
sdb_download(
  doi = "10.57760/sciencedb.o00115.00098",
  user_path = "~/Desktop"
)
```
